\section{Glossary}
\begin{description}

\item [Bendpoint] Bendpoint is a point, which functions as a control point for parametric curves allowing “bending” of said curve.

\item [Bézier-curve] Bézier-curve is a parametric curve, where shape is defined by blend of different control points.

\item [Canvas] The graphical view of the editors.

\item [Catmull-rom] Catmull-rom splines are a family of cubic interpolating splines formulated such that tangent at each point of the spline is calculated using the previous and next point on the spline. 

\item [Connector] Connector serves as either first or the last point of line.

\item [Eclipse] Eclipse is a integrated development environment, with extensive plug-in system for environment customization.

\item [Editor] Is a program used to manipulate information.

\item [ePNK] Eclipse Petri Net Kernel.

\item [Factory design pattern] Pattern where objects are created, so that the interface that calls the factory will decide which class to create.

\item [Geometry object] Geometry object can be either point or line.

\item [GUI] Graphical User Interface

\item [Hashmap] Hashmap is a data structure where values are mapped to keys.

\item [Input Point] Input Point is a point, where user is allowed to add tokens during the simulation.

\item [Interface] Interface is an abstract type that classes must implement.

\item [Javadoc standard] Format used by Javadoc is the industry standard for documenting Java classes.

\item [JMonkey] JMonkey is a 3D game engine written in and for java.

\item [Parametric curve] Parametric curve is a mathematical curve defined by point locations.

\item [Petri net] A mathematical and graphical model for the description of distributed systems. It is a directed bipartite graph, in which nodes represent transitions and places. The directed arcs describe which places are pre- and/or post-conditions for which transitions.

\item [Point] Point is a coordinate location in a two dimensional plane.

\item [Plug-in] Plug-in is a software component that adds specific feature to an existing software application.

\item [Simulation] Simulation is the imitation of operation of a real world process or system.

\item [Token] Petri net element which moves along the Petri net places through transitions.

\item [UML] Unified Modeling Language - standardized, general-purpose modeling language in the field of software engineering.

\item [Use case] A list of steps defining interactions between a role (e.g. "technical user"), also known as an actor, and a system for achieving a goal. The actor can be a human or an external system.

\item [Tool palette] A view on the graphical editors that has all the available editing tools for the editors.

\item [Technical/non-technical user] User either has or doesn't have prior technical knowledge of the subject.



 \end{description}
